---
title: "Homework 8 Presentation"
author: "Cal and Evan"
date: "10/11/2018"
output: ioslides_presentation
widescreen: TRUE
runtime: shiny
---
```{r, setup, include = FALSE}
library(tidyverse)
library(AER)
data = diamonds
```

***

```{r, echo = FALSE}
inputPanel(
  selectInput("Fill", label = "Diamond Variable:",
              choices = c("Diamond Clarity" = "clarity",
                          "Diamond Color" = "color",
                          "Quality of Cut" = "cut"), selected = "clarity"),
  radioButtons("xvar", label = "X Variable:",
               choices = c("Price" = "price", 
                                        "Carat" = "carat"),
               selected = "price"),
  sliderInput("dollar", label = "Price Range:",
              min = 0, max = 20000, value = c(0, 20000), step = 500),
  sliderInput("carrot", label = "Carat Range:",
              min = 0, max = 2.6, value = c(0, 2.6), step = .2)
  )

renderPlot({
    ggplot(data = filter(diamonds, 
                         price > input$dollar[1] &
                          price < input$dollar[2],
                         carat > input$carrot[1] &
                           carat < input$carrot[2])) +
    geom_histogram(mapping = aes_string(x = input$xvar, 
                                        fill = input$Fill)) +
    labs(
      title = "Data from Diamonds Dataset",
      x = "XVar Choice",
      y = "Diamond Count"
    )
  })
```

***

New Stuff that we used:

- Able to choose x-variable
  -Set x to vary with the radio button choice
  
  radioButtons("xvar", label = "X Variable",
  choices = c("Price" = "price",
  "Carat" = "carat"), selected = "price")
  
-Able to set range of values based on x variables
  - Had to filter diamond dataset to conform to our x variable length, otherwise get     error saying it's incorrect length
  
  sliderInput("name for r", label = "Title for Presentation",
              min = x1, max = x2, value(range1, range2), step = seperation value)